RJObject Manual

### 2015-12-07 Documents/manual.tex
Refer to paper

\section{Introduction}
RJObject is a C++ library for implementing certain kinds of trans-dimensional
hierarchical models (basically `mixture models')in DNest3. I developed this
library after realising that many models I was implementing all had this
common structure.
Throughout this manual, I will assume you're proficient at
DNest3. If not, please read the manual for that project first.

>>>>

\section{Introduction}
RJObject is a C++ library for implementing certain kinds of trans-dimensional
hierarchical models (basically `mixture models') in DNest3. I developed this
library after realising that many models I was implementing all had this
common structure.
Throughout this manual, I will assume you're proficient at
DNest3. If not, please read the manual for that project first and get some
experience using the software. I'll also assume you've read the RJObject
paper (available at {\tt http://arxiv.org/abs/1411.3921}).
